\textit{MSF: Modulated Sub-graph Finder}

### 2018-02-22 MSF_Paper_FA.tex
Conclusion updated

The connected modulated sub-graphs from 6hpi are shown in~(Fig.~2). The sub-graph shows different colors for the predefined  KEGG pathways and how they are connected to each other. The RIG-like receptor signaling in connected to Toll-like receptor, which intern connects to MAPK signaling, JAK-STAT signalling, CYtokine-cytokine signaling, Chemokine receptor signaling and TNF signaling. These pathways could be seen further leading to WNT Signaling, P13K-Akt signaling.

@@

Please state what you think are the main conclusions that can be
realistically drawn from the findings in the paper, taking care not to
make claims that cannot be supported.

@@

We thank all our colleagues who provided insight and expertise that greatly assisted the research and all reviewers for their constructive criticism.

\newpage

@@

>>>>

The connected modulated sub-graphs from 6hpi are shown in~(Fig.~2). The sub-graph shows different colors for the predefined  KEGG pathways and how they are connected to each other. The KEGG enrichment and visualization on the modulated sub-graph was done using StringApp~\cite{StringApp} in Cytoscape. The sub-graph shows RIG-like receptor signaling is connected to Toll-like receptor, which intern connects to MAPK signaling, JAK-STAT signalling, Cytokine-cytokine signaling, Chemokine receptor signaling and TNF signaling. These pathways could be seen further leading to WNT Signaling and P13K-Akt signaling.

@@

\textbf{MSF} is a fast and robust tool to find modulated sub-graphs from a given network. So far, it is the only tool from existing approaches that builds the modulated sub-graph from scratch using the network and DEG, where the predefined pathways could be seen connected to each other. The Robustness analysis shows that \textbf{MSF} is robust against noise and thus finds core modulated sub-graphs even if the DGEA is not carried out properly. Alongside with \textbf{MSF}, we provide a good directed cell signaling network.

@@

We thank all our colleagues who provided insight and expertise that greatly assisted the research and all reviewers for their constructive criticism. \newpage

@@

	\bibitem{StringApp}
	http://apps.cytoscape.org/apps/stringapp
